Unshuffling Permutations

### 2016-02-04 new-article.tex
LATIN 2016

>>>>

\begin{definition}[Property $\mathbf{P_1}$]
  \label{definition:Property P_1}
  Let $\pi$ be a permutation and $\vv{\mathcal{M}}$ be an oriented perfect
  matching of the linear graph $G_\pi$.
  $\vv{\mathcal{M}}$ is said to have property $\mathbf{P_1}$ if it avoids
  \InclusionLL,~\InclusionLR,~\InclusionRL,~\InclusionRR,~\CrossingLR
  and \CrossingRL.
\end{definition}

\begin{definition}[Property $\mathbf{P_2}$]
  \label{definition:Property P_2}
  Let $\pi$ be a permutation and $\vv{\mathcal{M}}$ be an oriented perfect
  matching of the linear graph $G_\pi$.
  $\vv{\mathcal{M}}$ is said to have property $\mathbf{P_2}$ if,
  for any two distinct arcs $(a, a')$ and $(b, b')$ in $\vv{\mathcal{M}}$,
  we have $\pi(a) < \pi(b)$ if and only if $\pi(a') < \pi(b')$.
\end{definition}

\begin{lemma}
  \label{lemma:matching}
  Let $\pi$ be a permutation. The following statements are equivalent:
  \begin{enumerate}
    \item The permutation $\pi$ is a square.
    \item There exists an oriented perfect matching $\vv{\mathcal{M}}$
    of the linear graph $G_\pi$ that has properties $\mathbf{P_1}$ and
    $\mathbf{P_2}$.
  \end{enumerate}
\end{lemma}
